Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-24 main_paper.tex
Rewrite second mathematical result and start its proof
This commit rewrites the second mathematical result and restates
it as a theorem that the 'double bootstrap' procedure accurately
approximates the asymptotic distribution of the bias-corrected
statistic we propose in Theorem and Algorithm 1.

This commit also has the first draft of a proof of the second
theorem as well as a crucial supporting lemma that actually
proves normality. There are still some steps missing and some
of the scaling factors are not yet correct. So there's work to
be done!

In the typical sharp RD setting, a researcher wishes to estimate the local 
causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
the potential outcomes for unit $i$ given it receives treatment and
 in the absence of treatment, respectively. Hence, the observed sample is 
 comprised of the running variable, $X_{i}$, and
 \begin{align}
  Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
 \end{align}
where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
define
 \begin{align}
  \mu(x)= \E[Y_{i}|X_{i}=x]
 \end{align}
Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
derivative of the unknown regression function and define 
$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
In most cases the population parameter of interest is 
$\tau=\E[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect
at the threshold). Under continuity and smoothness conditions on both the 
conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
the cutoff, $\tau$ is nonparametrically identifiable (Hahn, Todd and Van der 
Klaauw, 2001) by:
\begin{align}
 \tau&= \mu_{+}- \mu_{-} \nonumber \\ 
&\text{ where } \mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x),\text{ and } 
\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)
\end{align}

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\E[Y(1)|X=x]$ and $\E[Y(0)|X=x]$
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
\cite{calonico2014},\footnote{Throughout the paper we follow the
notation on CCT very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\1\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.

@@

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_n$ be the bandwidth used to estimate the local polynomial of
  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to
    hold as $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\V[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

@@

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}
Two results follow. The first is that the secondary bootstrap step produces
a consistent estimator of the bias under the bootstrap distribution. The
second is that the intervals overall are asymptotically valid.

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}

\begin{theorem}\label{T2}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A2} hold. Then
  \begin{equation}
    \label{eq:4}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

@@

\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
\end{equation*}

The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:5}
  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:6}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed

>>>>

In the typical sharp RD setting, a researcher wishes to estimate the local 
causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
the potential outcomes for unit $i$ given it receives treatment and
 in the absence of treatment, respectively. Hence, the observed sample is 
 comprised of the running variable, $X_{i}$, and
 \begin{align}
  Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
 \end{align}
where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
define
 \begin{align}
  \mu(x)= \E[Y_{i} \mid X_{i}=x]
 \end{align}
Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
derivative of the unknown regression function and define 
$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
In most cases the population parameter of interest is 
$\tau=\E[Y(1)-Y(0) \mid X=\bar{x}]$ (i.e., the average treatment effect
at the threshold). Under continuity and smoothness conditions on both the 
conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
the cutoff, $\tau$ is nonparametrically identifiable
$\tau = \mu_{+}- \mu_{-}$
where $\mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x)$ and
$\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)$
(Hahn, Todd and Van der Klaauw, 2001)

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\E[Y(1) \mid X=x]$ and $\E[Y(0) \mid X=x]$
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
local linear regressions in neighborhoods on both
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
\cite{calonico2014},\footnote{Throughout the paper we follow the
notation on CCT very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{h_n > X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= \argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\1\{0 > X_{i} > -h_n \}(Y_{i}-b_{0}-X_{i}b_{1})^{2}
\end{align*}

@@

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_n$ be the bandwidth used to estimate the local linear model and let
  $b_n$ be the bandwidth used for a local quadratic model. Then
  $n h_n \to \infty$, $n b_n \to \infty$, $n h_n^5 b_n^2 \to 0$, and
  $n b_n^5 h_n^2 \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
  V(h_{n}) &=\V[\tau(h_{n}) \mid X_1,\dots,X_n]
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

@@

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}

Theorem~\ref{T2} establishes that this ``bootstrap-within-bootstrap''
approximates the asymptotic distribution of the bias-corrected
statistic proposed by Algorithm~\ref{Alg1} and justifies this second
algorithm.

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather}
    \label{eq:4}
    \V^*(\hat\tau^{*} - \Delta^{**})/V(h_n,b_n) \to^p 1
  \intertext{and}
  \label{eq:5}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*} - \Delta^{**} - \tau^* \leq x ]
    - \Pr[\hat\tau - \Delta^* - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather}
\end{theorem}

@@

\newpage\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:6}
  \E^* \hat\mu_{\pm}^*(h_n) - \mu_{\pm}^{*} =
  h_n^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h_n)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
We can repeat the steps from Theorem~\ref{T1}'s proof to show that
\begin{align*}
  \hat\tau^* - \Delta^{**} - \tau^* &= (\hat\tau^* - \E^* \hat \tau^*) +
  (\E^* \hat \tau^* - \tau^*) - (\E^{**} \hat \tau^{**} - \tau^{**}) \\
  &= \hat\tau^* - \E^*\hat\tau^*
   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2.
\end{align*}
Consequently, the asymptotic behavior of
$\hat\tau^* - \Delta^** - \tau^*$ is determined by the behavior of
$\hat\tau^* - \E^*\hat\tau*$ and
$\hat\mu_{\pm}^{*(2)} - \mu_\pm^{*(2)}$ and these random variables are
weighted averages of the sums
\begin{equation*}
  \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^*
\end{equation*}
with $Z_i = (1, X_i, X_i^2)'$. By construction,
\begin{equation*}
  \V^*\Big(\ssum{i}{b_n} Z_i \varepsilon_i^* \Big)
  = \hat\sigma_\pm^2(b_n) \Gamma_\pm(b_n)
\end{equation*}
almost surely, making~\eqref{eq:4} a consequence of CCT's SA?.

For~\eqref{eq:5}, since $\hat\tau - \Delta^*$ is itself asymptotically
normal, it suffices to prove the pointwise result
\begin{equation}
  \label{eq:8}
  \Big\rvert \Pr^*[(\hat\tau^{*} - \Delta^{**} - \tau^*)
  / V^{1/2}(h_n,b_n) \leq x ] - \Phi(x)] \Big\lvert \to^p 0.
\end{equation}
for all $x$. Since the limiting distribution is continuous, an
argument attributed to Poly\'a immediately extends the pointwise
convergence result to the uniform result stated in~\eqref{eq:5}. (See
van der vaart, p. for the details of the argument.) But~\eqref{eq:8}
follows from Lemma~\ref{L1} as well, completing the proof.\qed

\subsection{Supporting results}

\begin{lemma}\label{L1}
  Define $Z_i = (1, X_i, X_i^2)$.  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{equation}
    \label{eq:9}
    \Big\rvert \Pr^*\Big[ \Gamma_\pm(b_n)^{-1/2}
    \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^* / \hat\sigma_\pm(b_n) < x \Big]
    - \Phi(x) \Big\lvert \to^p 0.
  \end{equation}
\end{lemma}

\begin{proof}
  Let $z_i = \alpha' Z_i$ for an arbitrary nonzero $\alpha$ and define
  $\gamma_\pm(b_n) = \alpha'\Gamma_\pm(b_n)\alpha$. We will
  establsh asymptotic normality for the scalar $z_i \varepsilon_i^*$;
  the multivariate case follows via the Cram\'er-Wold device. (cite
  van der vaart.)

  Define the filtration
  \begin{equation}
    \label{eq:10}
    \Fc_j^{*\pm} = \sigma(Y_1,\dots,Y_n; X_1,\dots,X_n;
    \varepsilon_{i_1}^{*\pm},\dots,\varepsilon_{i_j}^{*\pm})
  \end{equation}
  where the values $i_1, i_2,\dots, i_{M_h^{\pm}}$ form an ordering of
  all of the elements of $I_n^\pm$. (The specific order is
  unimportant.) Then
  $\{z_{i_j} \varepsilon_{i_j}^{*\pm}, \Fc_j^{*\pm}\}$ is a martingale
  difference sequence and~\eqref{eq:9} holds if
  \begin{equation}
    \label{eq:11}
    \savg{i}{h} z_{i}^2 \varepsilon_{i}^{*\pm\,2} -
    \gamma_{\pm}^*(b_n) \hat\sigma
    \to^p 0
  \end{equation}
  and, for all
  $\delta > 0$,
  \begin{equation}
    \label{eq:12}
    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
    \mid \Fc_{j-1}^{\pm}) \to^p 0.
  \end{equation}
  (cite Hall and Heyde.)

  For~\eqref{eq:11}, observe that
  $\{z_{i_j}^2 (\varepsilon_{i_j}^{*2} - \hat\sigma^2_\pm(b_n)), \Fc_j^\pm\}$
  is also a martingale difference sequence so convergence follows from
  the LLN.

  For~\eqref{eq:12}, we have
  \begin{align*}
    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
    \mid \Fc_{j-1}^{\pm})
    &= \oavg{i}{h_n} z_i^2 \oavg{j}{b_n} \hat\varepsilon_{j}^{\pm 2}
      \1\{\hat\varepsilon_{j}^{\pm 2} > \delta M_n^{\pm} / z_i^2 \} \\
  \end{align*}
  (Finish with: $\varepsilon_i^2$ is uniformly integrable,
  $\hat\varepsilon_i^2$ gets arbitrarily close to $\varepsilon_i^2$)
\end{proof}
